Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-07-07 manuscript.Rmd
Add page numbers for block quotes
Fix typos and tweet counter

\noindent The important story about the 2011
Arab revolts in Tunisia, Egypt, and Libya is not how the globalization of the
norms of civic engagement shaped the protesters' aspirations. Nor is it about
how activists used technology to share ideas and tactics. Instead, the critical
issue is how and why these ambitions and techniques resonated in their various
local contexts.

@@

\noindent a religious or linguistic minority
might suffer disproportionately in a given society, and this form of
aggrievement can lead to unrest across the social lines that distinguish the
minority group. Therefore, while collective cohesion is a function of targeted
maldistributions, it is individual penury that allows for this collective
mobilization.

@@

```{r cohesion-in-tweets, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = "A visual representation of cohesion in tweets. The shared content words--either identical or semantically similar--constitute a theme around which cohesion is occuring.", out.width='100%'}

@@

At the same time, the foundational theoretical assumptions of a linear world has
been increasingly replaced by ideas from dynamical systems theory. Rather than a
chain of events, time series data can be thought of as nested occurrences, where
mutually constrained parts (e.g., citizens, governments, real-world events,
social media platforms) are constantly interacting, leading to more global
behaviors that are larger than the sum of the parts [@turvey2018lectures]. When
analyzed as dynamical systems, many phenomena exhibit new nonlinear patterns
that were formerly overlooked. Nonlinear methods provide means for capturing the
rich temporal dynamics and variability that unfold in time series data.

@@

The corpus of tweets used included `r sum(cohesion_df$n)` Syrian tweets
occurring between March 30--June 15, 2012. Using the Twitter streaming API,
servers at the University of Texas at Austin collected the tweets. The servers
were run on a stable (LTS) version of Ubuntu Linus (v. 10.04) and were connected
directly to the high-bandwidth UT network maintained by IT services.

@@

```{r plot-rp-targ, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Recurrence plot (RP) for social cohesion and count of all events from target filtered data.', out.width='100%'}

@@

```{r plot-rp-source-targ, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Recurrence plot (RP) for social cohesion and count of all events from source and target filtered data.', out.width='100%'}

>>>>

\noindent The important story about the 2011
Arab revolts in Tunisia, Egypt, and Libya is not how the globalization of the
norms of civic engagement shaped the protesters' aspirations. Nor is it about
how activists used technology to share ideas and tactics. Instead, the critical
issue is how and why these ambitions and techniques resonated in their various
local contexts. (p. 2)

@@

\noindent a religious or linguistic minority
might suffer disproportionately in a given society, and this form of
aggrievement can lead to unrest across the social lines that distinguish the
minority group. Therefore, while collective cohesion is a function of targeted
maldistributions, it is individual penury that allows for this collective
mobilization. (p. 323)

@@

```{r cohesion-in-tweets, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = "A visual representation of cohesion in tweets. The shared content words--either identical or semantically similar--constitute a theme around which cohesion is occurring.", out.width='100%'}

@@

At the same time, the foundational theoretical assumptions of a linear world have
been increasingly replaced by ideas from dynamical systems theory. Rather than a
chain of events, time series data can be thought of as nested occurrences, where
mutually constrained parts (e.g., citizens, governments, real-world events,
social media platforms) are constantly interacting, leading to more global
behaviors that are larger than the sum of the parts [@turvey2018lectures]. When
analyzed as dynamical systems, many phenomena exhibit new nonlinear patterns
that were formerly overlooked. Nonlinear methods provide means for capturing the
rich temporal dynamics and variability that unfold in time series data.

@@

```{r num-tweets, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE}

num_tweets <- read.csv("./data/raw/Syria-social_cohesion.csv")

The corpus of tweets used included `r sum(num_tweets$n)` Syrian tweets
occurring between March 30--June 15, 2012. Using the Twitter streaming API,
servers at the University of Texas at Austin collected the tweets. The servers
were run on a stable (LTS) version of Ubuntu Linus (v. 10.04) and were connected
directly to the high-bandwidth UT network maintained by IT services.

@@

```{r plot-rp-targ, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Recurrence plot (RP) for social cohesion and counts of events from target filtered data.', out.width='100%'}

@@

```{r plot-rp-source-targ, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Recurrence plot (RP) for social cohesion and counts of events from source and target filtered data.', out.width='100%'}
